---
title: "2_Analysis"
author: "Sofie McComb"
date: "10/17/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

This script will analyze the results of the Circuitscape and Linkage Mapper Runs. Visualizations of the results will be created in ArcGIS.
The GIS file where the runs were completed is Data/2_Analysis/Circuitscape/KitFox_RunAnalyses_Revisions.mxd folder. KitFoxCoreAreas.mxd was used in the creation of Western Kern core areas. KitFox_CompareOutputs.mxd is just a quick check of different analysis outputs. Paper_Maps has the visualizations of results with the mxd used to make the pngs and some of the calculations that were completed to create the maps.

##Circuitscape
The ArcGIS Circuitscape toolbox (Circuitscape_for_ArcGIS_2013_10_08_rev2) was used to run the analyses. For Circuitscape, an ASCII file of the Kit Fox core area shapefile data was created using the focal area to raster tool in the Circuitscape toolbox (works better than creating ASCII in R). These are saved in the Data/1_DataProcessing/CoreArea folder for each year (ASCII created using each separate year resistance ASCII layer). Circuitscape was run for each resistance layer with each matching core area ASCII file. Ran pairwise analysis for cumulative current, and other settings standard.

Toolbox and results from the run saved in folder above the R project, and run on local drive where possible, for better processing.


##Linkage Mapper
The ArcGIS Linkage Mapper toolbox (Linkage_Mapper_2_0_0) was used to run the linkage mapper analyses. For Linkage Mapper, the resistance rasters and the kit fox core area shapefiles were used. For settings, ran cost-weighted distance analyses, dropped corridors that intersect core areas, and truncated corridors at 200 km.

Toolbox and results from the run saved in folder above the R project, and run on local drive where possible, for better processing.


##Pinchpoint Mapper
For Pinchpoint Mapper, ran on linkage mapper output with same core areas shapefile and resistance ASC used. For settings, used CWD cutoff distance of 200 km, and calculated adjacent pair pinch points using Circuitscape.



##Read Packages
```{r packages}

library(sf)
library(raster)
library(tidyverse)
library(ggplot2)
library(purrr)
library(estimatr)
library(reshape2)
library(broom)
library(gtools)
library(dotwhisker)
# library(coin)
# library(pwr)
# library(WRS2)


options(scipen = 999)

```

#Create Data Frames from LCPS

Go through all the connectivity analyses output (baseline eq1, b eq3, b eq5, negative exponetial c0.25, ne c4, ne c8) and create csv of dataframes

##### Does OG mean original here?
```{r og}

#Create csv dataframe from LCP Circuitscape outputs
    #Read in Least Cost Paths from Circuitscape/Linkage Mapper Runs
      #Originally run on local drive and moved into main project folder (not R project as very large)
      #Will need to change destinations to wherever files are stored using files below
    
files<-"Z:/FallowFox/ConnectivityTools/Results/Revisions/"
    
  #Original aka Old Version
  #######################################
    LCP_2011_csv<-sf::st_read(paste0(files, "KF_2011/output/link_maps.gdb"), layer = "KF_2011_LCPs") %>% st_set_geometry(NULL)%>% 
      dplyr::mutate(Year=2011) %>% select(Year, everything())
    LCP_2015_csv<-sf::st_read(paste0(files, "KF_2015/output/link_maps.gdb"), layer = "KF_2015_LCPs") %>% st_set_geometry(NULL)%>% 
      dplyr::mutate(Year=2015)%>% select(Year, everything())
    LCP_2017_csv<-sf::st_read(paste0(files, "KF_2017/output/link_maps.gdb"), layer = "KF_2017_LCPs") %>% st_set_geometry(NULL)%>% 
      dplyr::mutate(Year=2017)%>% select(Year, everything())
    write_csv(LCP_2011_csv, "Data/2_Analysis/LCP_CSV/LCP_2011_csv_old.csv")
    write_csv(LCP_2015_csv, "Data/2_Analysis/LCP_CSV/LCP_2015_csv_old.csv")
    write_csv(LCP_2017_csv, "Data/2_Analysis/LCP_CSV/LCP_2017_csv_old.csv")
    
    
  #Baseline eq1
  #######################################
    LCP_2011_csv_beq1<-sf::st_read(paste0(files, "KF_2011_base_eq1/output/link_maps.gdb"), layer = "KF_2011_base_eq1_LCPs") %>% st_set_geometry(NULL)%>% 
      dplyr::mutate(Year=2011) %>% select(Year, everything())
    LCP_2015_csv_beq1<-sf::st_read(paste0(files, "KF_2015_base_eq1/output/link_maps.gdb"), layer = "KF_2015_base_eq1_LCPs") %>% st_set_geometry(NULL)%>% 
      dplyr::mutate(Year=2015)%>% select(Year, everything())
    LCP_2017_csv_beq1<-sf::st_read(paste0(files, "KF_2017_base_eq1/output/link_maps.gdb"), layer = "KF_2017_base_eq1_LCPs") %>% st_set_geometry(NULL)%>% 
      dplyr::mutate(Year=2017)%>% select(Year, everything())
    write_csv(LCP_2011_csv_beq1, "Data/2_Analysis/LCP_CSV/LCP_2011_csv_beq1.csv")
    write_csv(LCP_2015_csv_beq1, "Data/2_Analysis/LCP_CSV/LCP_2015_csv_beq1.csv")
    write_csv(LCP_2017_csv_beq1, "Data/2_Analysis/LCP_CSV/LCP_2017_csv_beq1.csv")
    
  #Baseline eq3
  #######################################
    LCP_2011_csv_beq3<-sf::st_read(paste0(files, "KF_2011_base_eq3/output/link_maps.gdb"), layer = "KF_2011_base_eq3_LCPs") %>% st_set_geometry(NULL)%>% 
      dplyr::mutate(Year=2011) %>% select(Year, everything())
    LCP_2015_csv_beq3<-sf::st_read(paste0(files, "KF_2015_base_eq3/output/link_maps.gdb"), layer = "KF_2015_base_eq3_LCPs") %>% st_set_geometry(NULL)%>% 
      dplyr::mutate(Year=2015)%>% select(Year, everything())
    LCP_2017_csv_beq3<-sf::st_read(paste0(files, "KF_2017_base_eq3/output/link_maps.gdb"), layer = "KF_2017_base_eq3_LCPs") %>% st_set_geometry(NULL)%>% 
      dplyr::mutate(Year=2017)%>% select(Year, everything())
    write_csv(LCP_2011_csv_beq3, "Data/2_Analysis/LCP_CSV/LCP_2011_csv_beq3.csv")
    write_csv(LCP_2015_csv_beq3, "Data/2_Analysis/LCP_CSV/LCP_2015_csv_beq3.csv")
    write_csv(LCP_2017_csv_beq3, "Data/2_Analysis/LCP_CSV/LCP_2017_csv_beq3.csv")
    
  #Baseline eq5
  #######################################
    LCP_2011_csv_beq5<-sf::st_read(paste0(files, "KF_2011_base_eq5/output/link_maps.gdb"), layer = "KF_2011_base_eq5_LCPs") %>% st_set_geometry(NULL)%>% 
      dplyr::mutate(Year=2011) %>% select(Year, everything())
    LCP_2015_csv_beq5<-sf::st_read(paste0(files, "KF_2015_base_eq5/output/link_maps.gdb"), layer = "KF_2015_base_eq5_LCPs") %>% st_set_geometry(NULL)%>% 
      dplyr::mutate(Year=2015)%>% select(Year, everything())
    LCP_2017_csv_beq5<-sf::st_read(paste0(files, "KF_2017_base_eq5/output/link_maps.gdb"), layer = "KF_2017_base_eq5_LCPs") %>% st_set_geometry(NULL)%>% 
      dplyr::mutate(Year=2017)%>% select(Year, everything())
    write_csv(LCP_2011_csv_beq5, "Data/2_Analysis/LCP_CSV/LCP_2011_csv_beq5.csv")
    write_csv(LCP_2015_csv_beq5, "Data/2_Analysis/LCP_CSV/LCP_2015_csv_beq5.csv")
    write_csv(LCP_2017_csv_beq5, "Data/2_Analysis/LCP_CSV/LCP_2017_csv_beq5.csv")
  

  #Negative Exponental c0.25
  #######################################
    LCP_2011_csv_ne25<-sf::st_read(paste0(files, "KF_2011_ne_25/output/link_maps.gdb"), layer = "KF_2011_ne_25_LCPs") %>% st_set_geometry(NULL)%>% 
      dplyr::mutate(Year=2011) %>% select(Year, everything())
    LCP_2015_csv_ne25<-sf::st_read(paste0(files, "KF_2015_ne_25/output/link_maps.gdb"), layer = "KF_2015_ne_25_LCPs") %>% st_set_geometry(NULL)%>% 
      dplyr::mutate(Year=2015)%>% select(Year, everything())
    LCP_2017_csv_ne25<-sf::st_read(paste0(files, "KF_2017_ne_25/output/link_maps.gdb"), layer = "KF_2017_ne_25_LCPs") %>% st_set_geometry(NULL)%>% 
      dplyr::mutate(Year=2017)%>% select(Year, everything())
    write_csv(LCP_2011_csv_ne25, "Data/2_Analysis/LCP_CSV/LCP_2011_csv_ne25.csv")
    write_csv(LCP_2015_csv_ne25, "Data/2_Analysis/LCP_CSV/LCP_2015_csv_ne25.csv")
    write_csv(LCP_2017_csv_ne25, "Data/2_Analysis/LCP_CSV/LCP_2017_csv_ne25.csv")
    
  #Negative Exponental c4
  #######################################
    LCP_2011_csv_ne4<-sf::st_read(paste0(files, "KF_2011_ne_4/output/link_maps.gdb"), layer = "KF_2011_ne_4_LCPs") %>% st_set_geometry(NULL)%>% 
      dplyr::mutate(Year=2011) %>% select(Year, everything())
    LCP_2015_csv_ne4<-sf::st_read(paste0(files, "KF_2015_ne_4/output/link_maps.gdb"), layer = "KF_2015_ne_4_LCPs") %>% st_set_geometry(NULL)%>% 
      dplyr::mutate(Year=2015)%>% select(Year, everything())
    LCP_2017_csv_ne4<-sf::st_read(paste0(files, "KF_2017_ne_4/output/link_maps.gdb"), layer = "KF_2017_ne_4_LCPs") %>% st_set_geometry(NULL)%>% 
      dplyr::mutate(Year=2017)%>% select(Year, everything())
    write_csv(LCP_2011_csv_ne4, "Data/2_Analysis/LCP_CSV/LCP_2011_csv_ne4.csv")
    write_csv(LCP_2015_csv_ne4, "Data/2_Analysis/LCP_CSV/LCP_2015_csv_ne4.csv")
    write_csv(LCP_2017_csv_ne4, "Data/2_Analysis/LCP_CSV/LCP_2017_csv_ne4.csv")
    
  #Negative Exponental c8
  #######################################
    LCP_2011_csv_ne8<-sf::st_read(paste0(files, "KF_2011_ne_8/output/link_maps.gdb"), layer = "KF_2011_ne_8_LCPs") %>% st_set_geometry(NULL)%>% 
      dplyr::mutate(Year=2011) %>% select(Year, everything())
    LCP_2015_csv_ne8<-sf::st_read(paste0(files, "KF_2015_ne_8/output/link_maps.gdb"), layer = "KF_2015_ne_8_LCPs") %>% st_set_geometry(NULL)%>% 
      dplyr::mutate(Year=2015)%>% select(Year, everything())
    LCP_2017_csv_ne8<-sf::st_read(paste0(files, "KF_2017_ne_8/output/link_maps.gdb"), layer = "KF_2017_ne_8_LCPs") %>% st_set_geometry(NULL)%>% 
      dplyr::mutate(Year=2017)%>% select(Year, everything())
    write_csv(LCP_2011_csv_ne8, "Data/2_Analysis/LCP_CSV/LCP_2011_csv_ne8.csv")
    write_csv(LCP_2015_csv_ne8, "Data/2_Analysis/LCP_CSV/LCP_2015_csv_ne8.csv")
    write_csv(LCP_2017_csv_ne8, "Data/2_Analysis/LCP_CSV/LCP_2017_csv_ne8.csv")

```

# Within estimator regression

Loop through dataframes for different resistance layers and create/save within estimator regression summaries

### Loop through Within estimator regression
```{r withinReg}

#Read in and loop through dataframes
q<-c("old", "beq1", "beq3", "beq5", "ne25", "ne4", "ne8")
dir.create("Data/2_Analysis/df_reg/", showWarnings = FALSE)

#Loop through different resistance layer connectivity outputs and run regression models and create df of model results
for (c in q){
  print(c)
  dir.create(paste0("Data/2_Analysis/Stats/", c, "/"), showWarnings = FALSE)  
    #Dataframe
    ##################################################################
    
    # Organize into one dataframe
    df_2011 <- read_csv(paste0("./Data/2_Analysis/LCP_CSV/LCP_2011_csv_",c ,".csv"))
    df_2015 <- read_csv(paste0("./Data/2_Analysis/LCP_CSV/LCP_2015_csv_",c ,".csv"))
    df_2017 <- read_csv(paste0("./Data/2_Analysis/LCP_CSV/LCP_2017_csv_",c ,".csv"))
    df_reg <- rbind(df_2011, df_2015, df_2017)
    
    # Create to_from factor variable column
    df_reg$From_To <- as.factor(paste0(df_reg$From_Core,"_",df_reg$To_Core))
    df_reg$Year <- as.factor(df_reg$Year)
    
    # Convert meters to KM
    df_reg$CW_Dist_km <- df_reg$CW_Dist/1000
    df_reg$LCP_Length_km <- df_reg$LCP_Length/1000
    df_reg$Euc_Dist_km <- df_reg$Euc_Dist/1000
    
    #Save df_reg
    
    write_csv(df_reg, paste0("Data/2_Analysis/df_reg/df_reg_", c, ".csv"))
    
    # Summarizations
    df_summary<-df_reg %>% 
      group_by(Year) %>% 
      summarize(LCP=n(), 
                CWDmean=mean(CW_Dist_km), CWDsd=sd(CW_Dist_km),
                LCPLengthmean=mean(LCP_Length_km),LCPLengthsd=sd(LCP_Length_km),
                CWDLCPmean=mean(cwd_to_Path_Length_Ratio),CWDLCPsd=sd(cwd_to_Path_Length_Ratio),
                ERmean=mean(Effective_Resistance), ERsd=sd(Effective_Resistance))
    
    head(df_summary)
    write_csv(df_summary, paste0("./Data/2_Analysis/Stats/",c, "/df_summary.csv"))
    
    #Regressions
    ##################################################################
    
    ####### CWD Distance #######
    # Reference year: 2011
    df_reg <- within(df_reg, Year <- relevel(Year, ref = '2011'))
    CWD_lmrob <- lm_robust(formula = CW_Dist_km ~ Year,
              data = df_reg,
              clusters = From_To,
              fixed_effects = ~From_To,
              se_type = 'stata')
    # Reference year: 2015
    df_reg <- within(df_reg, Year <- relevel(Year, ref = '2015'))
    CWD_lmrob15 <- lm_robust(formula = CW_Dist_km ~ Year,
              data = df_reg,
              clusters = From_To,
              fixed_effects = ~From_To,
              se_type = 'stata')
    
    ###### LCP Length ######
    # Reference year: 2011
    df_reg <- within(df_reg, Year <- relevel(Year, ref = '2011'))
    lcp_length_km_lmrob <- estimatr::lm_robust(formula = LCP_Length_km ~ Year,
              data = df_reg,
              clusters = From_To,
              fixed_effects = ~From_To,
              se_type = 'stata')
    # Reference year: 2015
    df_reg <- within(df_reg, Year <- relevel(Year, ref = '2015'))
    lcp_length_km_lmrob15 <- lm_robust(formula = LCP_Length_km ~ Year,
              data = df_reg,
              clusters = From_To,
              fixed_effects = ~From_To,
              se_type = 'stata')
  
    
    ####### CWD to Path Length Distance #######
    # Reference year: 2011
    df_reg <- within(df_reg, Year <- relevel(Year, ref = '2011'))
    CWDtoLCP_lmrob <- lm_robust(formula = cwd_to_Path_Length_Ratio ~ Year,
              data = df_reg,
              clusters = From_To,
              fixed_effects = ~From_To,
              se_type = 'stata')
    # Reference year: 2015
    df_reg <- within(df_reg, Year <- relevel(Year, ref = '2015'))
    CWDtoLCP_lmrob15 <- lm_robust(formula = cwd_to_Path_Length_Ratio ~ Year,
              data = df_reg,
              clusters = From_To,
              fixed_effects = ~From_To,
              se_type = 'stata')
    
    
    ###### Effective Resistance ######
    # Reference year: 2011
    df_reg <- within(df_reg, Year <- relevel(Year, ref = '2011'))
    ER_lmrob <- lm_robust(formula = Effective_Resistance ~ Year,
              data = df_reg,
              clusters = From_To,
              fixed_effects = ~From_To,
              se_type = 'stata')
    # Reference year: 2015
    df_reg <- within(df_reg, Year <- relevel(Year, ref = '2015'))
    ER_lmrob15 <- lm_robust(formula = Effective_Resistance ~ Year,
              data = df_reg,
              clusters = From_To,
              fixed_effects = ~From_To,
              se_type = 'stata')
     
    
    #Print summary result
    sink(paste0("./Data/2_Analysis/Stats/",c, "/lm_summary.txt"))
    summary(CWD_lmrob)
    summary(CWD_lmrob15)
    summary(lcp_length_km_lmrob)
    summary(lcp_length_km_lmrob15)
    summary(CWDtoLCP_lmrob)
    summary(CWDtoLCP_lmrob15)
    summary(ER_lmrob)
    summary(ER_lmrob15)
    sink() # returns output to the console

    #clean-up and combine lm results into dataframe
    
    models <- list(CWD_lmrob = CWD_lmrob, CWD_lmrob15 = CWD_lmrob15,
                   lcp_length_km_lmrob = lcp_length_km_lmrob, lcp_length_km_lmrob15 = lcp_length_km_lmrob15, 
                   CWDtoLCP_lmrob = CWDtoLCP_lmrob, CWDtoLCP_lmrob15 = CWDtoLCP_lmrob15,
                   ER_lmrob = ER_lmrob, ER_lmrob15 = ER_lmrob15)
    models_df<-purrr::map_df(models, broom::tidy, .id = "model") %>% 
      dplyr::filter(!term=="Year2011") %>% 
      dplyr::mutate(term=ifelse(model=="lcp_length_km_lmrob15"|model=="CWD_lmrob15"|
                                   model=="CWDtoLCP_lmrob15"|model=="ER_lmrob15", "2015-2017",
                                 ifelse(term=="Year2015", "2011-2015", "2011-2017"))) %>% 
      dplyr::mutate(Metric=ifelse(outcome=="LCP_Length_km", "LCP (km)", 
                                  ifelse(outcome=="CW_Dist_km", "CWD (km)",
                                         ifelse(outcome=="cwd_to_Path_Length_Ratio", "CWD to Path Length Ratio",
                                                "Effective Resistance (Ohms)")))) %>% 
      dplyr::mutate(model=c) %>%  #Info on resistance version
       dplyr::mutate(PvalSig=gtools::stars.pval(p.value))
    write_csv(models_df, paste0("./Data/2_Analysis/Stats/",c, "/lm_df.csv"))
    
   
} #End For Loop

```



#Dot & Whisker Plots of Within-Estimator Results

```{r dataViz}

#Read in & rbind all df_reg csvs
  list_of_files <- list.files(path = "./Data/2_Analysis/Stats",
                              recursive = TRUE,
                              pattern = "\\lm_df.csv$",
                              full.names = TRUE)
  modelsdfs <- list_of_files %>%
      set_names() %>% 
      map_df(read_csv)  

#Rename models
  modelnames<-data.frame(model=c("old", "beq1", "beq3", "beq5", "ne25", "ne4", "ne8"), 
                       modelnames=c("Original","Linear Eq1", "Linear Eq3", "Linear Eq5", "Negative Exponential 0.25", "Negative Exponential 4", "Negative Exponential 8"))
  modelsdfs<-modelsdfs %>% merge(modelnames, by="model")%>% dplyr::select(-model) %>% dplyr::rename(model=modelnames) %>% select(model, everything())

#Reorder groups
  modelsdfs$Metric <- factor(modelsdfs$Metric,      # Reordering group factor levels
                         levels = c("CWD (km)" , "LCP (km)", "CWD to Path Length Ratio", "Effective Resistance (Ohms)"))

#Save csv for plots
  write_csv(modelsdfs, paste0("./Data/2_Analysis/Stats/lm_df_all.csv"))

modelsdfs <- read_csv("./Data/2_Analysis/Stats/lm_df_all.csv")
  
#Dot and Whisker Plots
  modelsdfs %>% dotwhisker::dwplot()+
    theme_bw()+ 
    xlab("Coefficient Estimate")+
    geom_vline(xintercept = 0, colour = "grey60", linetype = 2)+
    scale_y_discrete(limits = c("2011-2015","2011-2017","2015-2017"))+
    coord_flip()+
    facet_wrap(~Metric, scales="free")+
    theme(legend.title=element_blank())+
    scale_color_brewer(palette="Set2")
    

 #Save plot 
  ggsave("./Data/2_Analysis/Stats/ModelComparison.jpg")


```










Paired t-test below--come back to this
Because just going to do one example for SI



## New DFs for paired t-tests (Ashley reshapes data and keeps in one table instead)
```{r new_dfs}

df_2011 <- read_csv("./Data/2_Analysis/LCP_CSV/LCP_2011_csv.csv") %>%
  select(Year,
         To_Core,
         From_Core,
         ER_2011=Effective_Resistance,
         CWD_2011=CW_Dist,
         CWDtoLCP_2011=cwd_to_Path_Length_Ratio) %>%
  mutate(From_To = as.factor(paste0(From_Core,"_",To_Core)),
         CWD_km_2011 = CWD_2011/1000)

df_2015 <- read_csv("./Data/2_Analysis/LCP_CSV/LCP_2015_csv.csv") %>%
    select(Year,
         To_Core,
         From_Core,
         ER_2015=Effective_Resistance,
         CWD_2015=CW_Dist,
         CWDtoLCP_2015=cwd_to_Path_Length_Ratio) %>%
  mutate(From_To = as.factor(paste0(From_Core,"_",To_Core)),
         CWD_km_2015 = CWD_2015/1000)

df_2017 <- read_csv("./Data/2_Analysis/LCP_CSV/LCP_2017_csv.csv") %>%
    select(Year,
         To_Core,
         From_Core,
         ER_2017=Effective_Resistance,
         CWD_2017=CW_Dist,
         CWDtoLCP_2017=cwd_to_Path_Length_Ratio) %>%
  mutate(From_To = as.factor(paste0(From_Core,"_",To_Core)),
         CWD_km_2017 = CWD_2017/1000)

df_ttests <- merge(df_2011,df_2015,by='From_To') %>%
  merge(.,df_2017,by="From_To") %>%
  select(1,5:8,12:15,19:22)

```

# Paired T.Tests
```{r paired_t_tests}

attach(df_ttests)
# names(df_ttests)
# Effective Resistance vs 2011
t.test(ER_2011,ER_2015,paired = TRUE)
t.test(ER_2011,ER_2017,paired = TRUE)
t.test(ER_2015,ER_2017,paired = TRUE)

# CWD
t.test(CWD_km_2011,CWD_km_2015,paired = TRUE)
t.test(CWD_km_2011,CWD_km_2017,paired = TRUE)
t.test(CWD_km_2015,CWD_km_2017,paired = TRUE)

# LCP to CWD
t.test(CWDtoLCP_2011,CWDtoLCP_2015,paired = TRUE)
t.test(CWDtoLCP_2011,CWDtoLCP_2017,paired = TRUE)
t.test(CWDtoLCP_2015,CWDtoLCP_2017,paired = TRUE)
detach(df_ttests)
```

# Example results comparison: Within estimator regression versus T.tests on same sample with LCP to CWD ratio as outcome variable
```{r Ttest_reg_comparison}

# Subset regression dataset to only include paths that are also in the df_ttests set of From_To paths
df_reg_2 <- filter(df_reg,From_To %in% df_ttests$From_To)

# T.test
df_reg_2 <- within(df_reg_2, Year <- relevel(Year, ref = '2015'))
CWDtoLCP_lmrob <- lm_robust(formula = cwd_to_Path_Length_Ratio ~ Year,
          data = df_reg_2,
          clusters = From_To,
          fixed_effects = ~From_To,
          se_type = 'stata')
summary(CWDtoLCP_lmrob)

t.test(df_ttests$CWDtoLCP_2011,df_ttests$CWDtoLCP_2015,paired = TRUE)
t.test(df_ttests$CWDtoLCP_2011,df_ttests$CWDtoLCP_2017,paired = TRUE)
t.test(df_ttests$CWDtoLCP_2015,df_ttests$CWDtoLCP_2017,paired = TRUE)
```


