---
title: "2b_withinEstimator"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### Packages and data
```{r packages_and_data}
rm(list=ls())

library(tidyverse)
library(lme4)
library(lmtest)
library(lfe)
library(plm)
library(clubSandwich)
library(estimatr)

df_2011 <- read_csv("./Data/2b_WithinEstimator/LCP_2011_csv.csv")
df_2015 <- read_csv("./Data/2b_WithinEstimator/LCP_2015_csv.csv")
df_2017 <- read_csv("./Data/2b_WithinEstimator/LCP_2017_csv.csv")

df_full <- rbind(df_2011, df_2015, df_2017)

# Create to_from factor variable column
df_full$From_To <- as.factor(paste0(df_full$From_Core,"_",df_full$To_Core))
df_full$Year <- as.factor(df_full$Year)

# Convert meters to KM
df_full$CW_Dist_km <- df_full$CW_Dist/1000
df_full$LCP_Length_km <- df_full$LCP_Length/1000
df_full$Euc_Dist_km <- df_full$Euc_Dist/1000

```

### Within estimator regresssion
```{r within_reg}

ER_areg <- felm(Effective_Resistance ~ Year | From_To | 0 | From_To, 
                data = df_full)

# Matching coeffecients
ER_areg$coefficients
# Not matching SEs
ER_areg$se
# Still not matching
clubSandwich::coef_test(ER_areg,vcov = "CR2",cluster = df_full$From_To)

# 
# CWD_areg <- felm(CW_Dist_km ~ Year | From_To | 0 | From_To, data = df_full)
# coeftest(CWD_areg)
# 
# CWDtoLCP_areg <- felm(cwd_to_Path_Length_Ratio ~ Year | From_To | 0 | From_To, data = df_full)
# coeftest(CWDtoLCP_areg)

```


### plm and clubSandwich: Here we get the same values for the coeffecients and constant/intercept, but different SEs
```{r within_clubSand}

ERwithPLM = plm(Effective_Resistance ~ Year, data = df_full, 
                      index = c("From_To"),
                      model=c("within"))
summary(ERwithPLM)
ERwithPLM_intercept = plm::within_intercept(ERwithPLM)

# SEs don't match
coef_test(ERwithPLM, vcov = "CR2",cluster = df_full$From_To)
```


### estimatr: Here we get coefficients and SEs that match Ashley's, but I can't find a way to get the model intercept
```{r withEstimatrpackage}

# ###### LCP Length ######
# lcp_length_km_lmrob <- estimatr::lm_robust(formula = LCP_Length_km ~ Year,
#           data = df_full,
#           clusters = From_To,
#           fixed_effects = ~From_To,
#           se_type = 'stata')
# 

# summary(lcp_length_km_lmrob)


# df_full <- within(df_full, Year <- relevel(Year, ref = '2015'))
# lcp_length_km_lmrob15 <- lm_robust(formula = LCP_Length_km ~ Year,
#           data = df_full,
#           clusters = From_To,
#           fixed_effects = ~From_To,
#           se_type = 'stata')
# summary(lcp_length_km_lmrob15)
# 
# 
# ####### CWD Distance #######
# df_full <- within(df_full, Year <- relevel(Year, ref = '2011'))
# CWD_lmrob <- lm_robust(formula = CW_Dist_km ~ Year,
#           data = df_full,
#           clusters = From_To,
#           fixed_effects = ~From_To,
#           se_type = 'stata')
# summary(CWD_lmrob)
# 
# 
# ####### CWD to Path Length Distance #######
# df_full <- within(df_full, Year <- relevel(Year, ref = '2011'))
# CWDtoLCP_lmrob15 <- lm_robust(formula = cwd_to_Path_Length_Ratio ~ Year,
#           data = df_full,
#           clusters = From_To,
#           fixed_effects = ~From_To,
#           se_type = 'stata')
# summary(CWDtoLCP_lmrob15)
# 
# 
###### Effective Resistance ######
df_full <- within(df_full, Year <- relevel(Year, ref = '2011'))
ER_lmrob <- lm_robust(formula = Effective_Resistance ~ Year,
          data = df_full,
          clusters = From_To,
          fixed_effects = ~From_To,
          se_type = 'stata')

# Matching coefs and SEs, but no intercept
summary(ER_lmrob)

# 
# df_full <- within(df_full, Year <- relevel(Year, ref = '2015'))
# ER_lmrob15 <- lm_robust(formula = Effective_Resistance ~ Year,
#           data = df_full,
#           clusters = From_To,
#           fixed_effects = ~From_To,
#           se_type = 'stata')
# summary(ER_lmrob15)


```

######## All good below here ########

## New DFs for paired t-tests (Ashley reshapes data and keeps in one table instead)
```{r new_dfs}
# 
# df_2011 <- read_csv("./Data/2b_WithinEstimator/LCP_2011_csv.csv") %>% 
#   select(Year,
#          To_Core,
#          From_Core,
#          ER_2011=Effective_Resistance,
#          CWD_2011=CW_Dist, 
#          CWDtoLCP_2011=cwd_to_Path_Length_Ratio) %>% 
#   mutate(From_To = as.factor(paste0(From_Core,"_",To_Core)),
#          CWD_km_2011 = CWD_2011/1000)
# 
# df_2015 <- read_csv("./Data/2b_WithinEstimator/LCP_2015_csv.csv") %>% 
#     select(Year,
#          To_Core,
#          From_Core,
#          ER_2015=Effective_Resistance,
#          CWD_2015=CW_Dist, 
#          CWDtoLCP_2015=cwd_to_Path_Length_Ratio) %>% 
#   mutate(From_To = as.factor(paste0(From_Core,"_",To_Core)),
#          CWD_km_2015 = CWD_2015/1000)
# 
# df_2017 <- read_csv("./Data/2b_WithinEstimator/LCP_2017_csv.csv") %>% 
#     select(Year,
#          To_Core,
#          From_Core,
#          ER_2017=Effective_Resistance,
#          CWD_2017=CW_Dist, 
#          CWDtoLCP_2017=cwd_to_Path_Length_Ratio) %>% 
#   mutate(From_To = as.factor(paste0(From_Core,"_",To_Core)),
#          CWD_km_2017 = CWD_2017/1000)
# 
# df_full <- merge(df_2011,df_2015,by='From_To') %>% 
#   merge(.,df_2017,by="From_To") %>% 
#   select(1,5:8,12:15,19:22)

```

# Paired T.Tests
```{r paired_t_tests}
# 
# # attach(df_full)
# # names(df_full)
# # Effective Resistance vs 2011
# t.test(ER_2011,ER_2015,paired = TRUE)
# t.test(ER_2011,ER_2017,paired = TRUE)
# t.test(ER_2015,ER_2017,paired = TRUE)
# 
# # CWD
# t.test(CWD_km_2011,CWD_km_2015,paired = TRUE)
# t.test(CWD_km_2011,CWD_km_2017,paired = TRUE)
# t.test(CWD_km_2015,CWD_km_2017,paired = TRUE)
# 
# # LCP to CWD
# t.test(CWDtoLCP_2011,CWDtoLCP_2015,paired = TRUE)
# t.test(CWDtoLCP_2011,CWDtoLCP_2017,paired = TRUE)
# t.test(CWDtoLCP_2015,CWDtoLCP_2017,paired = TRUE)
```


